---
title: "JOUR8500 WeekXX Demo Problem Set"
author: "YOUR NAME"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE
)
```

## Step 1 - Audience Engagement and News Coverage

This paragraph describes a **research question** about news media.

We are interested in whether *negative tone* and *political slant* increase audience engagement.

- Political slant
- Emotional tone
- Breaking news
- Visuals

Our hypotheses are:

1. More negative articles will receive more engagement.
2. More politically extreme articles will receive more engagement.
3. Breaking news articles will receive more engagement than non-breaking articles.

For more information, see [Journal of Communication](https://academic.oup.com/joc).

R code should look like this:

```{r}
1 + 1
```

You should click **Knit** and then upload both .Rmd and the resulting .html file to Canvas. Also, you can "Knit" to PDF if you prefer that format.

## Step 2 - XXX

Type your code here:

```{r}
# YOUR CODE HERE
```

YOUR ANSWER HERE