---
title: "JOUR8500 Week03 qualtRics Package Demo Problem Set (Completed)"
author: "Carolina Aguiar, Isabel Garlough-Shah, Ruiheng Sun"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE
)
```

# Overview


This problem set introduces a basic run down of installing the `qualtRics` package, how to use API keys in Qualtrics, importing data directly from Qualtrics to R, and practice filtering data.


# Step 1 Installing and loading qualtRics

The packages we will use include:
- `qualtRics`: for retrieve a data set from Qualtrics
- `tidyverse`, `dplyr`, `tidyr`,`psych`: for data selection

Steps:

1. Install them using `install.packages()`

2. Load them into your library using `library()`

```{r}
# install.packages("qualtRics")
# install.packages("tidyverse")
# install.packages("dplyr")
# install.packages("tidyr")
# install.packages("psych")

library(qualtRics)
library(tidyverse)
library(dplyr)
library(tidyr)
library(psych)
```

# Step 2 Import data

To import data directly from Qualtrics into R, we first need to register the **Qualtrics API credentials** with the qualtRics R package so that R can securely communicate with the Qualtrics account. 

Steps:
First use the code `qualtrics_api_credentials()` and then in the brackets fill in the code `api_key =`. 

After the equal sign, fill in the API key "Iq3etyjeqW28MpNq9AkPbl02xqLa50ALfmmzrygf".

To find your personal API key navigate to Account settings, scroll down to the API header and click the `Generate Token` button


After inputting the API key, in the next line of code you will use the code `base_url =` and fill in "yul1.qualtrics.com". To find your personal base url navigate to Account settings, scroll down to the User header, and locate Datacenter ID. Here you will see a 2-3 letter and number code (e.g., az1, co1, eu1). From here your base URL will be in the format: "[2-3 letter and number code].qualtrics.com"


In the next line of code input `install = TRUE` and in the line after that input `overwrite = TRUE` and end the bracket. In the final line of code input `surveys <- all_surveys()` to load all the surveys.

```{r}
qualtrics_api_credentials(api_key = "Iq3etyjeqW28MpNq9AkPbl02xqLa50ALfmmzrygf",
                          base_url = "yul1.qualtrics.com",
                          install = TRUE,
                          overwrite = TRUE)
surveys <- all_surveys()
```

Use `?fetch_survey()` to find the code template.

Finally, to import the survey data into R, use the `fetch_survey()` function. Inside the function use the `surveyID` argument to search the `surveys$id[which(surveys$name=="NameofSurvery"`. Fill in the name of the survey "AI CAN HELP_Study2_Main". This line of code extracts this specific survey from `surveys` object (generated earlier with `all_surveys()`) and the survey's unique ID. 


In the next 5 lines you will add additional arguments to control for how the data is downloaded: `verbose = TRUE` shows a progress bar during the download, `force_request = TRUE` ensures a fresh pull from Qualtrics rather than cached data, `include_display_order = FALSE` removes question order metadata, `label = FALSE` keeps the original Qualtrics variable names, and `convert = FALSE` imports the data in its raw format. Finally create an object at the beginning of this code entitled `data_main` to label the data set. 

```{r}
data_main <- fetch_survey(surveyID = surveys$id[which(surveys$name=="For R - The Role of Generative AI in Overcoming Ideological Bias in News Consumption - Copy")], 
                    verbose = TRUE,
                    force_request = TRUE,
                    include_display_order = FALSE,
                    label = F,
                    convert = F)
```

# Step 3 Filter data

After connecting with Qualtrics dataset, we are able to explore some features.

For example, we want to filter out participants based on time.

### Check time zone

First, we need check which time zone is attached to the StartDate column in the dataset, using`attr(x, which)`

- x means the column you want to select: `data_main$StartDate`
- which is the name of the specific piece of information you want to extract: `"tzone"` (you need the double quotation marks)
- If the result shows `"America/Chicago"`, you are correct!

Also, check `?attr()` for more information

```{r}
attr(data_main$StartDate, "tzone")
```

### Filter out participants based on your criteria

Next, we filter out participants who start after Oct 12th, 2024, 10am.

- Use `data_main[data_main$StartDate, ]` to select subset data
- After `data_main$StartDate`, use `as.POSIXct(x, tz = ""),` to compare the time zone

Also, check `?as.POSIXct()` for more information

```{r}
data_start <- data_main[data_main$StartDate >= as.POSIXct("2024-10-12 10:00:00", tz = "America/Chicago"),]
```

We also want to include participants who finish

- Use column `Progress` and it should be 100

```{r}
data_progress <- data_main[data_main$Progress==100,]
```

We want to see how many participants see FOX in the column `Stimuli_AA`

```{r}
data_AA <- data_main[data_main$Stimuli_AA == "FOX", ]
```

Keep only the ro where the `prolific_id` value is present (not missing)

- Use `is.na()` for missing values

```{r}
data_prolific_id <- data_main[is.na(data_main$prolific_id)==F,]
```

### Other notes

- Change the Qualtrics question name so that the variable name in R is easy to understand.
- Use "_" instead of a space in a variable name.
- Recode values on Qualtrics.



