---
title: "W8_igraph_demo"
author: "Jiarou, Kaiyi, Qiling"
date: "2026-03-14"
references: https://kateto.net/network-visualization/
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: false
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE
)
```

## Contents

1.  Building a network
2.  Describing a network
3.  Layout & Highlighting

### Building a network

**Social network**: a set of social entities, such as people, groups,
and organizations, with some relationships or interactions between them
(Tabassum et al., 2018) 

-   Vertices/Nodes: social entities, e.g.,individuals, groups, organizations
-   Edges/Links: ties between entities

```{r}
setwd("D:/UMN/26spring/Computational social methods/W9/Data_files")
```


```{r}
# install.packages("igraph")
library(igraph)
```

-   Step 1: data preparation

    -   The data used here includes network of hyperlinks and mentions
        among news sources
    -   nodes: includes ID (must), other features we are interested in,
        e.g., name, audience size... (optional)
    -   links: includes the source ("from") and target ("to") (must),
        other features we are interested in, e.g., weight, types (optional)

    ```{r}
    nodes <- read.csv("Dataset1-Media-Example-NODES.csv", header = T, as.is = T)
    links <- read.csv("Dataset1-Media-Example-EDGES.csv", header=T, as.is=T)
    # different way of reading data
    # nodes <- read.csv(file.choose(), header = TRUE, as.is = TRUE)
    # links <- read.csv(file.choose(), header = TRUE, as.is = TRUE)
    ```

```{r}
# have a quick look
head(nodes)
head(links)
```

-   Step 2: Creating an igraph object

```{r}
net <- graph_from_data_frame(d=links, vertices=nodes, directed=T) 
net
```

From "IGRAPH b3af137 DNW- 17 49 -- ", we can read some basic features of
this network 

-   D/U: Directed or Undirected 

-   N: the nodes have Names

-   W: the edges are Weighted 

-   B: for a bipartite (two-mode) graph (where nodes have a type attribute) - 
not included in this network


-   "17": the number of nodes; "49": the number of edges

-   the format of attributes: name (action object/data type) : e.g., 
    
    - media (v/c): it describes a vertex-level attribute, it is a character 
    
    - (g/c): graph-level, character - (e/n): edge-level, numeric


-   Step 3: Describing the network (overall)

```{r}
plot(net) # a bit ugly
```

```{r}
find("simplify")
```

```{r}
net_simple <- igraph::simplify(
  net,
  remove.multiple = FALSE,
  remove.loops = TRUE
)

#if remove.multiple = TRUE
#simplify(
  #net,
  #remove.multiple = TRUE,
  #remove.loops = TRUE,
  #edge.attr.comb = list(weight = "sum", type = "ignore") #If there are multiple edges between A and B, these edges will be "merged" into one. For "weight" attribute, add the weights of multiple edges. For "type" attribute, discard them.
#)

```

```{r}
# We can reduce the arrow size and remove the labels
plot(net_simple, edge.arrow.size=.4,vertex.label=NA) # a bit better
```

-   Some overall indicators to describe the network

1.  *Density*: Existing number of connections/Possible number of
    connections

-   the degree of closeness of internal connections within a group
-   if Density = 1, it means that all entities are connected

```{r}
edge_density(net, loops=F)
```

2.  *Average Path Length*: The average number of steps required between
    any two entities in the network

-   The smaller this number is, the faster the information spreads in
    this network

```{r}
mean_distance(net, directed=T)

avg_dist <- mean_distance(net, directed=T, weights=NA)
print(avg_dist)
```

3.  *Diameter*: The shortest path length between the two farthest
    entities on the network

```{r}
diameter(net, directed=T, weights=NA)
```

4.  *Transitivity/Clustering Coefficient*: the degree to which nodes in
    a graph tend to cluster together

```{r}
#global transitivity: the number of closed triplets (or 3 x triangles) over the total number of triplets (both open and closed)
#closed triplets: A-B,B-C,A-C
#open triplets: A-B,B-C
transitivity(net, type="global")
```

```{r}
#local transitivity: The probability that the neighbors of a entity are themselves connected
transitivity(net, type="local")
```

### Problem set

### Task for practice: Build a network and describe its overall characteristics

Please use the "Airlines" data

1.  Building the network

```{r}

```

2.  Calculate the overall indicators

-   Density

```{r}

```

-   Average Path Length

```{r}

```

-   Diameter

```{r}

```

-   Transitivity

```{r}

```

### Node-level centrality measures

Centrality measures help us identify which nodes are more important in
the network from different perspectives. Here we introduce four common
node-level indicators: degree centrality, closeness centrality,
betweenness centrality, and eigenvector centrality.

#### Degree centrality

Degree centrality measures how many direct connections a node has.

In a directed network, we can distinguish:

In-degree: how many ties a node receives

Out-degree: how many ties a node sends

Nodes with higher degree centrality are more directly connected to
others.

```{r}
# degree centrality
deg_all <- degree(net, mode = "all")
deg_in  <- degree(net, mode = "in")
deg_out <- degree(net, mode = "out")

# combine into a table
degree_result <- data.frame(
  media = V(net)$media,
  degree_all = deg_all,
  degree_in = deg_in,
  degree_out = deg_out
)

degree_result
```

```{r}
# show the top nodes by total degree
degree_result[order(-degree_result$degree_all), ]
```

#### Closeness centrality

Closeness centrality measures how close a node is to all other nodes in
the network based on shortest paths.

A node with high closeness centrality can reach other nodes more
quickly.

This may indicate faster access to information in the network.

```{r}
# closeness centrality
close_out <- closeness(net, mode = "out", normalized = TRUE)
close_in  <- closeness(net, mode = "in", normalized = TRUE)

closeness_result <- data.frame(
  media = V(net)$media,
  closeness_out = close_out,
  closeness_in = close_in
)

closeness_result
```

```{r}
# show the top nodes by out-closeness
closeness_result[order(-closeness_result$closeness_out), ]
```

#### Betweenness centrality

Betweenness centrality measures how often a node lies on the shortest
paths between other nodes.

Nodes with high betweenness may act as bridges or brokers.

They can play an important role in connecting different parts of the
network.

```{r}
# betweenness centrality
btw <- betweenness(net, directed = TRUE, normalized = TRUE)

betweenness_result <- data.frame(
  media = V(net)$media,
  betweenness = btw
)

betweenness_result
```

```{r}
# show the top nodes by betweenness
betweenness_result[order(-betweenness_result$betweenness), ]
```

#### Eigenvector centrality

Eigenvector centrality measures not only how many connections a node
has, but also how important its connected neighbors are.

A node connected to many well-connected nodes will have a higher
eigenvector centrality.

This indicator captures influence or prestige in the network.

```{r}
# eigenvector centrality
eig <- eigen_centrality(net, directed = TRUE, scale = TRUE)

eigen_result <- data.frame(
  media = V(net)$media,
  eigenvector = eig$vector
)

eigen_result
```

```{r}
# show the top nodes by eigenvector centrality
eigen_result[order(-eigen_result$eigenvector), ]
```

Combine all centrality measures in one table

```{r}
centrality_result <- data.frame(
  media = V(net)$media,
  degree_all = degree(net, mode = "all"),
  degree_in = degree(net, mode = "in"),
  degree_out = degree(net, mode = "out"),
  closeness_out = closeness(net, mode = "out", normalized = TRUE),
  closeness_in = closeness(net, mode = "in", normalized = TRUE),
  betweenness = betweenness(net, directed = TRUE, normalized = TRUE),
  eigenvector = eigen_centrality(net, directed = TRUE, scale = TRUE)$vector
)

centrality_result
```

#### Visualize degree centrality

We can also use node size to reflect degree centrality in the graph.

```{r}
V(net)$size <- degree(net, mode = "all") * 2 + 8
V(net)$label <- V(net)$media

plot(net,
     edge.arrow.size = .3,
     vertex.color = "lightblue",
     vertex.frame.color = "gray40",
     vertex.label.color = "black")
```

### Layout and highlighting

plotting parameters: we can set different parameters for nodes and
edges, such as colors, shapes, sizes, and labels. To specify graphical
parameters, we can supply name arguments to the plotting command
`plot()`. Parameters for vertices start with prefix `vertex.`,
parameters for edges have prefix `edge.` You can use `?igraph.plotting`
to get more information about parameters.

```{r}

?igraph.plotting

```

-   Step 1: Set parameters using `plot()` function

Plot with curved edges (`edge.curved=.1`) and reduce arrow size
(`edge.arrow.size=.4`).

```{r}

plot(net_simple, edge.arrow.size=.4, edge.curved=.1)

```

Set edge color to red (`edge.color =`), the node color to orange
(`vertex.color=`) and border color to yellow (`vertex.frame.color=`).
Replace the vertex label with the node names stored in "media"
(```` vertex.label= ```); set the label color to black ( ````vertex.label.color=
\`)

```{r}

plot(net_simple, edge.arrow.size=.2, edge.color="red",
     vertex.color="orange", vertex.frame.color="yellow", #set the border color of the nodes to white
     vertex.label=V(net_simple)$media, vertex.label.color="black") 

```

### Task for practice: visualize net_simple and adjust parameters

in the following code chunk, plot the net_simple using `plot()`
function. Set the edges as black with small arrows (.4). Set nodes to be
blue with gray borders. Make each node to display a label from the
variable `type.label`. Also adjust the labels to be yellow.

```{r}

```

-   Step 2: Network layouts

Network layouts are methods that decide the coordinates of each node,
where each node should appear when we draw a network. To explore and
demonstrate different layouts, we first create a 100-node graph using
`sample_pa()`. Using this function, the computer will automatically
generate a network showing 100 nodes and the edges (links between nodes.
This graph is based on preferential attachment (Barabasi-Albert model).

```{r}

net.bg <- sample_pa(100)  #create a network
V(net.bg)$size <- 8  #set the size of node to 8
V(net.bg)$frame.color <- "white" #set the border color
V(net.bg)$color <- "orange" #set the fill color of nodes
V(net.bg)$label <- ""  #remove node label
E(net.bg)$arrow.mode <- 0 #remove arrows for edges
plot(net.bg) 

```

Next, we will introduce several layout types. first, `layout_randomly`
helps place the nodes in random positions.`layout_in_circle` helps
arrange all the nodes in a circle. `layout_on_sphere` calculates
positions for each node as if the nodes were placed on the surface of a
sphere (a 3D ball).

```{r}
#layout randomly
plot(net.bg, layout=layout_randomly)

#layout nodes in circle
l <- layout_in_circle(net.bg)
plot(net.bg, layout=l)

#layout in 3d sphere
l <- layout_on_sphere(net.bg)
plot(net.bg, layout=l)

```

Fruchterman-Reingold is one of the most used force-directed layout
algorithms out there. We can use `layout_with_fr()` to plot the graph.
You can understand this function as to help us draw connected nodes
closer to each other while unconnected nodes appear far from each other.
Some other layout types include Kamada Kawai (kk), which is also a force
directed algorithm. kk is similar to fr. The function used for kk is
`layout_with_kk`. Another force-directed algorithm is GEM
(`layout_with_gem`). Graphopt is another force directed algorithm,
particularly helpful for visualizing large networks
(`layout_with_graphopt`). The MDS (multidimensional scaling) algorithm
is another layout type that places nodes that similar to and closer to
each other closer together in the graph (`layout_with_mds`).

```{r}

#Fruchterman-Reingold layout
l <- layout_with_fr(net.bg)
plot(net.bg, layout=l)

#Kamada Kawai layout
l <- layout_with_kk(net.bg)
plot(net.bg, layout=l)

#GEM layout
l <- layout_with_gem(net.bg)
plot(net.bg, layout=l)

#graphopt layout
l <- layout_with_graphopt(net.bg)
plot(net.bg, layout=l)

#MDS layout
plot(net.bg, layout=layout_with_mds)
```

The following codes show all the avaiable layouts in igraph.

```{r}

layouts <- grep("^layout_", ls("package:igraph"), value=TRUE)[-1] 
# Remove layouts that do not apply to our graph.
layouts <- layouts[!grepl("bipartite|merge|norm|sugiyama|tree", layouts)]

par(mfrow=c(3,3), mar=c(1,1,1,1))
for (layout in layouts) {
  print(layout)
  l <- do.call(layout, list(net)) 
  plot(net, edge.arrow.mode=0, layout=l, main=layout) }

```

-   Step 3: Highlight networks If our network structure is too dense, we
    cannot observe it carefully and extract the most important
    information. Sometimes we just want to highlight the most important
    ties in the graph. The first way is to sparsify the network, keeping
    only the most important ties (that of higher weight).

```{r}

hist(links$weight) #create a histogram of distribution of the weight
mean(links$weight) #calculate the mean value of the weight
sd(links$weight) #calculate the standard deviation of the weight

# Here, we only keep edges that have weight higher than the mean for the network
cut.off <- mean(links$weight) 
net.sp <- delete_edges(net, E(net)[weight<cut.off])
plot(net.sp, layout=layout_with_kk) 

```

Another way to highlight part of networks is to highlight a group of
particular nodes. Following is an example. In this example, we focus on
NYT and visualize distances from NTY in the graph.

```{r}

#calculate distances from NYT node
dist.from.NYT <- distances(net, v=V(net)[media=="NY Times"], 
                           to=V(net), weights=NA)

# Set colors to plot the distances:
oranges <- colorRampPalette(c("dark red", "gold")) #create a color scale from dark red to gold.
col <- oranges(max(dist.from.NYT)+1)
col <- col[dist.from.NYT+1] #assign colors to each node based on distances 

plot(net, vertex.color=col, vertex.label=dist.from.NYT, edge.arrow.size=.6, 
     vertex.label.color="white") #vertex.label shows the distance from NYT on each node.

```

Another way to highlight part of networks is to highlight a path in the
network. The following codes demonstrate an example to find the shortest
connection path between MSNBC and the New York Post and highlights it in
the network graph

```{r}

#find the shortest path between MSNBC and New York Post.
news.path <- shortest_paths(net, 
                            from = V(net)[media=="MSNBC"], 
                             to  = V(net)[media=="New York Post"],
                             output = "both") # both path nodes and edges

# Generate edge color variable to plot the path:
ecol <- rep("gray80", ecount(net)) #all edges are colored light gray
ecol[unlist(news.path$epath)] <- "orange" #change the color of those edges on the shortest path to orange
# Generate edge width variable to plot the path:
ew <- rep(2, ecount(net)) #create default edge width
ew[unlist(news.path$epath)] <- 4 #make the path edge width thicker
# Generate node color variable to plot the path:
vcol <- rep("gray40", vcount(net)) #create default node colors
vcol[unlist(news.path$vpath)] <- "gold" #change the color of the nodes on path

plot(net, vertex.color=vcol, edge.color=ecol, 
     edge.width=ew, edge.arrow.mode=0)
```

Another way to draw attention to a group of nodes (we saw this before
with communities) is to mark and highlight the group of nodes.

```{r}

par(mfrow=c(1,2)) #split the graph area into one row and two columns.
#mark one group
plot(net, mark.groups=c(1,4,5,8), mark.col="#C5E5E7", mark.border=NA) #highlight nodes 1,4,5,7 and cover them in light blue.

#mark two groups
plot(net, mark.groups=list(c(1,4,5,8), c(15:17)), #group nodes 1,4,5,8 and 15,17 separately.
          mark.col=c("#C5E5E7","#ECD89A"), mark.border=NA)
```
