---
title: "JOUR 8500 Tidyverse Demo"
author: "Quin & Namuun"
date: "`r Sys.Date()`"
output: html_document
---
# Install and load package libraries easily with {librarian}

While not a part of the {tidyverse} suite of R packages, librarian is very useful for sharing code (with new packages) easily with others in your scripts.

Our setup here will use librarian instead of the traditional library() list. We can avoid having to install multiple packages at once this way. You'll get a popup at the top of your RStudio that asks if you want to install missing packages listed in the shelf() command.

```{r setup, include=FALSE, echo = FALSE}
# set your working director with setwd(), 
# OR on the top bar under Session > Set Working Directory...


# Install {librarian} if you don't have it
library(librarian) # We use the traditional library() call to load librarian()
shelf(dplyr, tidyr, readr, stringr, forcats, lubridate) 
#But shelf() makes our lives easier -- list all the packages you want to include
# in the script!

# you can also simply call tidyverse's whole collection by including tidyverse
#in shelf() and it will load all of the core packages at once.

# readr (one of the tidyverse packages) is where read.csv() comes from!
# select the path for your media engagement data file
media <- read.csv(file = "Week02_media_engagement.csv")

media
```

# About Tidyverse

The official documentation website is here: <https://tidyverse.org/packages/>

Tidyverse isn't just one package, but includes a total of 9 packages. 
Each has a reference page linked which describe all of the different functions included!

- dplyr: <https://dplyr.tidyverse.org/reference/index.html> 
better grammar and piping for data manipulation.
- tidyr: <https://tidyr.tidyverse.org/reference/index.html> 
functions for tidying data, like pivoting and splitting columns into new ones.
- readr: <https://readr.tidyverse.org/reference/index.html> 
functions for reading in matrices like .csv files. To read in other file types like .xlsx or .dta (from Stata), you'll need separate packages for those.
- stringr: <https://stringr.tidyverse.org/reference/index.html> 
functions for parsing strings and extracting information from cells similar to LOOKUPS in Excel or other SQL/data management systems.
- forcats: <https://forcats.tidyverse.org/reference/index.html> 
functions for working with categorical or factor variables.
- lubridate: <https://lubridate.tidyverse.org/reference/index.html> 
functions for working with dates and times.
- the tibble, purrr and ggplot2 packages also automatically load with library(tidyverse), but those will be covered by others in class (especially ggplot2)

# Data & Piping Structure
- We'll reuse the data from Week 2 (Week02_media_engagement.csv)
- There are differences in how tidyverse uses piping compared to base R (which uses |>).
- Since R version 4.4.0(?) the native pipe operator works with all packages. HOWEVER, tidyverse code often uses "%>%" for its piping.

## dplyr: Viewing data with the tidy piping structure
dplyr has four main command functions that help us view and clean our data:

- select()
- filter()
- arrange()
- group_by()

And two commands that help us transform our data into new variables or summarize into new data.frames:

- mutate()
- summarize(), or summarise()

- *NOTE:* mutate() and summarize() are similar, but different: mutate() adds new columns to the dataset. summarize() will collapse down your data to smaller tables which are typically better for plotting and understanding your data.

Let's say we want to view our data by topic. So we should cut out some of the variables we aren't interested in or don't need.
- group_by is prioritized, so we group first
- then select columns we want to include in our tibble with select:
```{r include = TRUE}
#first call our data.frame:
media1 <- media %>%
  group_by(topic) %>%
  select(topic, date, outlet, outlet_type, frame_type, tone, slant,
         breaking, visuals, length_words)

media1
```

# Problem 1 (with dplyr): 
## Wrangling data & summarizing
- Summarize the mean length_words by topic among legacy_mainstream outlet types, and arrange them in descending order (highest mean to smallest).

## Requirements:
- Use filter(), group_by(), summarize() (or summarise()), and arrange()
- Name the output column mean_words
```{r include = TRUE}
# Create an object called media_e1
# Start from media1
# Filter to legacy_mainstream
# Group by topic
# Summarize mean length_words as mean_words
# Arrange descending by mean_words

# KEY
media_e1 <- media1 %>%
  group_by(topic) %>%
  filter(outlet_type == c("legacy_mainstream")) %>%
  summarize(mean_words = mean(length_words)) %>%
  arrange(desc(mean_words))
  
media_e1
```

# Problem 2 (with forcats): 
## Categorical variables & factoring
- forcats is great for handling categorical variables and relabeling/releveling (especially for plotting them properly).
- all forcats functions usually have a fct_*() structure.

Task: Create a new variable breaking_cha that converts breaking into "Yes" and "No".
Hint: Use factor() and fct_recode().

## Requirements:
- breaking_cha must be a factor
- Recode "0" -> "No" and "1" -> "Yes"
- Show your result with a select() that includes breaking_cha, breaking, and a few context columns

```{r include = TRUE}
# Create an object called media2a
# Start from media1
# Create breaking_cha using factor() + fct_recode() in mutate function
# Select breaking_cha, topic, date, outlet, outlet_type, frame_type, tone, slant, breaking, visuals, length_words

# KEY

# We almost always need to set the variable we want to mutate as a factor() 
# before messing with it further
# fct_recode is the most long-winded of the forcats functions,
# where you are changing the current values to new ones by hand
# NOTE: when reassigning, format as such: "[new var]" = "[old var]"
media2a <- media1 %>%
  mutate(breaking_cha = factor(breaking),
         breaking_cha = fct_recode(breaking_cha,
                                   "No" = "0",
                                   "Yes" = "1")
         ) %>%
  select(breaking_cha, topic, date, outlet, outlet_type, frame_type, tone, slant, breaking, visuals, length_words)
# selecting the columns we want to see, in the order we want them to be -- 
# and we'll more quickly see if our new "issues" column is there

media2a
```

You can also collapse variables into more broad categories with fct_collapse():

Here is an example of collapsing some of the topic variable into broader categories:
```{r include = FALSE}
media2b <- media1 %>%
  mutate(issues = factor(topic),
         issues = fct_collapse(topic,
                                "Political" = c("Elections", "Politics",
                                                "Foreign Policy", "Immigration",
                                                "Crime", "Education"),
                                "Socioeconomic" = c("Health", "Climate",
                                                    "Economy", "Technology")
                                )
         ) %>%
  select(issues, topic, date, outlet, outlet_type, frame_type, tone, slant, 
         breaking, visuals, length_words)
```

# Problem 3 (with stringr): 
## Extracting parts of an observation's text
- str_detect() is the most useful function from stringr (in my opinion), since it doesn't require implementing regular expressions to work well.

Let's say we want to look only at our digital outlet_types, regardless of what they cover (digital_politics, digital_viral, and digital_explainer).

- We can filter() from dplyr with str_detect() to look only at the outlet_types that contain "digital" observations into a new column:

**Task A:** Filter the dataset to keep only rows where outlet_type contains "digital".

**Task B:** Create a new variable outlet_medium:

"digital" if outlet_type contains "digital"

"other" otherwise

## Requirements:
- Use str_detect()
- Use filter()
- Use mutate() + case_when()

Select and print: outlet_medium, outlet_type, topic, outlet, slant, length_words

```{r include = TRUE}
# Task A
# Create an object called media2a
# Start from media1
# Filter to outlet_type values that contain "digital"

# KEY
# this is different than using filter alone,
# which would only take included observed variables one at a time
media3a <- media1 %>%
  filter(str_detect(outlet_type, "digital")) 
media3a
```

- and also create new categorical (or dummy) variables with mutate() and case_when() from dplyr, using str_detect().
- case_when() operates like your classic "if/else statement" in other coding or data wrangling programs.
```{r include = TRUE}
# Task B
# Create an object called media3b
# Start from media1
# Create outlet_medium using case_when() + str_detect()
# Select requested columns or variables

# KEY
media3b <- media1 %>%
# pulls all outlet_types that contain "digital" at once and labels them as such. 
  mutate(outlet_medium = case_when(str_detect(outlet_type, "digital") ~ "digital", 
# We can add other conditions in between, BUT add them from most to least specific.  
                                   .default = as.character("other") 
# .default arg sets the value for any variables that don't match any other conditions.
                                   )
  ) %>%
  select(outlet_medium, outlet_type, topic, outlet, frame_type, tone, slant, breaking, visuals, length_words)

media3b
```


# Problem 4 (with lubridate): 
## Parsing dates and times and pivoting to new columns

Let's say we want to be able to look at longitudinal patterns in the data aggregated by month and year (if we had multiple years in this data).
Well, as it stand with the media data.frame, we only have the date column...which is in YYYY-MM-DD (ymd) format.

- We can combine forcats and lubridate so R easily recognizes the date structure, and pulls out what we need to relevel the new variable.
- we can also use fct_relevel() to set the order in which the months should appear in figures, or tibbles with arrange().

## Create a dataset that:
1. Creates a month label from date
2. Orders months Jan–Dec
3. Groups by month and topic
4. Creates topic_count = n()
5. Selects: month, topic, topic_count, outlet, outlet_type, frame_type, tone, slant, breaking, visuals, length_words
6. Arranges by month

## Requirements:
- Use ymd()
- Use month(..., label = TRUE)
- Use fct_relevel() with the month order: Jan, Feb, Mar, ..., Dec

```{r include = TRUE}
# Create an object called media4a
# Start from media
# Convert date -> month label using ymd() and month(..., label = TRUE)
# Relevel months Jan-Dec
# Group by month and topic
# Create topic_count = n()
# Select columns or variables and arrange by month

# KEY

media4a <- media %>%
  mutate(month = factor(date),
         month = ymd(month), # converts month to a ymd() format date-time class object
         month = month(month, label = TRUE),
         month = fct_relevel(month, c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec")) # puts the months in order!
  ) %>%
  group_by(month, topic) %>%
  mutate(topic_count = n()) %>%
  select(month, topic, topic_count, outlet, outlet_type, frame_type, tone, slant, breaking, visuals, length_words) %>%
  arrange(month)
  
head(media4a)
```

# Problem 5 (tidyr + lubridate): Split and rebuild date
We can split a date column into components and then rebuild a proper Date.

**Task A:** Use separate() to split date into year, month, day.

**Task B:** Rebuild date using make_date(year, month, day).

## Requirements:
- Use separate(date, into = c("year","month","day"), sep = "-")

```{r}
# Task A
# Create media4b
# Start from media
# separate date into year/month/day

# KEY

# We can break apart the date column with tidyr using separate():
media4b <- media %>%
  separate(date, into = c("year", "month", "day"), sep = "-")

# note that the separated columns will maintain their type (character),
# and do not convert to a datetime structure from lubridate. 

# check result. note that the date column goes away!
# preview first rows of the data, or else it will show all the entries
head(media4b)

# Task B
# Create media4c
# Start with media4b
# rebuild date with make_date() in mutate function
# We can also break apart the date column with tidyr using separate():

# KEY

# We can reassemble the date column back together in a few ways:
# First using make_date():
media4c <- media4b %>%
  mutate(date = make_date(year = year, month = month, day = day))

# check result. the separated columns are maintained and the date column returns
head(media4c) 
```

