---
title: "JOUR 8500 Quanteda Demo"
author: Quin, Kaiyi, Stasi
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=true}
# setwd()
install.packages(librarian)

library(librarian)
shelf(tidyverse, quanteda, readxl) 
# load quanteda
# and readxl: a package that allows us to read .xlsx files

# the quanteda.dictionaries package requires devtools to install from GitHub.


# We can use some of my (Quin's) data: 
aian_snippets <- read_xlsx("Week04_aian_snippets.xlsx")
# This data contains closed caption snippets of evening, local TV news 
# from an initial keyword search for "American Indian" and "Alaska Native". 

# This dataset was sourced from the Wesleyan Media Project's partnership with TVEyes, a third party company who tracks network television video, audio, closed captions, and subsequent metadata throughout the United States (among other places).  

# I got permission from my collaborators at WMP to use this subset for class! So please don't share this data outside of the course :)

```

## About Quanteda

The official website is <https://quanteda.io/> and tutorials are available at <https://tutorials.quanteda.io/>
The Quanteda package includes functions that help researchers apply natural language processing to texts.

Quanteda has three basic types of objects:
-Corpus (tutorial: <https://tutorials.quanteda.io/basic-operations/corpus/>)
A Corpus helps to create a data frame that stores character strings of the actual text, as well as other document-level information, such as the author, date, and source of the text.

-Tokens (tutorial: <https://tutorials.quanteda.io/basic-operations/tokens/>)
With the `Tokens()` function, each document is stored as a vector of tokens. This means that, instead of storing one long character string (such as a sentence), the text is split into a list of separate tokens, such as words. You can remove white spaces, punctuation, and numbers using the `tokens()` function

-Document-feature-matrix (tutorial: <https://tutorials.quanteda.io/basic-operations/dfm/>)
A dfm stores how often each feature appears in each document. The frequencies of features in documents are stored in a matrix format. `dfm()` function constructs a document-feature matrix (DFM) from a tokens object. 

## Step 1: Creating a corpus() & docvars()
## A corpus is a specialized object that stores text documents along with the associated metadata. 
##i.e. a structured contained for text data that preserves (1) raw data text and (2) document-level info 
```{r include = TRUE}
### Creating a corpus from a character vector 
texts <- c(
  "Doc one", 
  "Doc two", 
  "Doc three", 
)
corp <- corpus(texts)
print(corp)

### Creating a corpus with document-level metadata (docvars) 
corp_meta <- corpus(texts, 
                    docvars = data.frame(
                      author = c("Alice", "Bob", "Charlie"), 
                      year = c(2020, 2021, 2022), 
                      category = c("news", "blog", "news")
                    ))
print(corp_meta)

##Access the texts
texts(corp_meta)

# Access document variables (metadata)
docvars(corp_meta)

# construct a corpus from "snippet" column in aian_snippets
aian_corpus <- corpus(aian_snippets, text_field = "snippet")
print(aian_corpus)
summary(aian_corpus, 5) #show the first 5 documents with all the docvars
docvars(aian_corpus)
```


## Step 2: Tokenization and Removing Stopwords
```{r include = TRUE}
##Before removing stopwords, tokenize the text and view the tokens 
aian_tokens <- tokens(aian_corpus, what = "word", 
                      remove_punct = TRUE, 
                      remove_symbols = TRUE, 
                      include_docvars = TRUE, 
                      verbose = TRUE) 
# verbose gives you some information while the tokenization is happening, and lets you know when it's done
# quanteda defaults to words, but some people may want to parse sentences, keep punctuation and/or symbols for other reasons.

##Remove English stopwords using quanteda's build-in list 
aian_tokens_sw <- tokens_select(aian_tokens, 
                                pattern = stopwords("en"),
                                selection = "remove")

print(aian_tokens_sw)
```


## Step 3: Creating a Dictionary with dictionary()
`dictionary()` is a function used to create a dictionary for text analysis. For example, `dictionary()` can be used to scan words, categorize them, and count how often each category appears. You can use `dictionary()` to create a dictionary object by your own by listing some character vectors. You can also import an existing dictionary file in formats such as WordStat, LIWC, Yoshikoder, Lexicoder, YAML.

If you use `dictionary()` to create your own dictionary. Inside `dictionary()`, we use `list()` to collect different categories of vectors. For example, if we want to create two categories, positive and negative, to categorize the text, we can write it as `dictionary(list(positive = ..., negative = ...))`. Inside each category, we use quotation marks (`""`)to specify multiple words under one category, for example: `dictionary(list(positive = c("happy", "smile"), negative = c("unhappy")))`. An asterisk (`*`) can be used to match all variations of a root word. For example, happ* can include happiness and happy.


``` {r include = TRUE}

# create a dictionary with school, art, and sports categories
dict_A<- dictionary(list(school = c("school*", "child*", "student*", "campus*"),
                       art = c("art*", "museum*", "perform*", "music*", "craft*"),
                       sport = c("mascot", "athlet*", "sport*")
                       ))
print(dict_A)

```

## Step 4: Applying the dictionary to our tokenized data
token_lookup() is the most flexible dictionary look up function in quanteda. Simply out, it is used to match tokens to a dictionary, check whether certain token appears in a dictionary. We can write it as `token_lookup(token object, dictionary = dictionary object)`.

Task: 
(1) Create a dictionary with two categories, school and art. The words that belong to school include school, child, student, and campus. The words that belong to art include art, museum, and perform.
(2) Apply the dictionary you created to a tokenized object
``` {r include = TRUE}

# apply token_lookup to the tokenized object
dict_toks <- tokens_lookup(toks_A, dictionary = dict_A)
print(dict_toks)

```



## Applying Dictionaries & Document-Feature Matrices with dfm()
- A Document-Feature matrix (DFM) provides frequencies of features (our dictionary keyword category groups) for each document (snippet) in our data.
- We can use DFMs to plot and visualize our data and help us analyze sentiments or the distribution of topics captured in a set of text-based data.

- To do this, we nest our tokens_lookup() object into our dfm() command

``` {r include = TRUE}
# The simplest way to apply our dfm:
aian_dfm <- dfm(tokens_lookup(aian_tokens, dict, valuetype = "glob", verbose = TRUE))

# We can also trim down our dfm with dfm_trim() to include only dictionary categories that have at least 1 dictionary term for at least 1 document.
aian_dfm_trim <- aian_dfm %>%
dfm_trim(min_termfreq = 1, min_docfreq = 1, verbose = TRUE)
  
# We could also group up our dfm by another variable for analysis.
aian_dfm_trim <- aian_dfm_group %>%
dfm_group(groups = MarketName, verbose = TRUE)


```


