---
title: "JOUR 8500 Quanteda Demo"
author: Quin, Kaiyi, Stasi
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=true}
# setwd()
install.packages(librarian)

library(librarian)
shelf(tidyverse, quanteda, readxl) 
# load quanteda
# and readxl: a package that allows us to read .xlsx files

# the quanteda.dictionaries package requires devtools to install from GitHub.


# We can use some of Quin's data: 
aian_snippets <- read_xlsx("Week04_aian_snippets.xlsx")
# This data contains closed caption snippets of evening, local TV news 
# from an initial keyword search for "American Indian" and "Alaska Native". 

# This dataset was sourced from the Wesleyan Media Project's partnership with TVEyes, a third party company who tracks network television video, audio, closed captions, and subsequent metadata throughout the United States (among other places).  

# I got permission from my collaborators at WMP to use this subset for class! So please don't share this data outside of the course :)

```

## About Quanteda

The official website is <https://quanteda.io/> and tutorials are available at <https://tutorials.quanteda.io/>
The Quanteda package includes functions that help researchers apply natural language processing to texts.

Quanteda has three basic types of objects:
-Corpus (tutorial: <https://tutorials.quanteda.io/basic-operations/corpus/>)
A Corpus helps to create a data frame that stores character strings of the actual text, as well as other document-level information, such as the author, date, and source of the text.

-Tokens (tutorial: <https://tutorials.quanteda.io/basic-operations/tokens/>)
With the `Tokens()` function, each document is stored as a vector of tokens. This means that, instead of storing one long character string (such as a sentence), the text is split into a list of separate tokens, such as words. You can remove white spaces, punctuation, and numbers using the `tokens()` function

-Document-feature-matrix (tutorial: <https://tutorials.quanteda.io/basic-operations/dfm/>)
A dfm stores how often each feature appears in each document. The frequencies of features in documents are stored in a matrix format. `dfm()` function constructs a document-feature matrix (DFM) from a tokens object. 

## Step 1: Creating a corpus() & docvars()
## A corpus is a specialized object that stores text documents along with the associated metadata. 
##i.e. a structured contained for text data that preserves (1) raw data text and (2) document-level info

Task:
(1) Create your corpus and subset the corpus into two new objects
```{r include = TRUE}

```


## Step 2: Tokenization and Removing Stopwords

Task: 
(1) Tokenize the corpus with corpus() and remove stopwords with tokens_select()
```{r include = TRUE}

```


## Step 3: Creating a Dictionary with dictionary()
`dictionary()` is a function used to create a dictionary for text analysis. For example, `dictionary()` can be used to scan words, categorize them, and count how often each category appears. You can use `dictionary()` to create a dictionary object by your own by listing some character vectors. You can also import an existing dictionary file in formats such as WordStat, LIWC, Yoshikoder, Lexicoder, YAML.

If you use `dictionary()` to create your own dictionary. Inside `dictionary()`, we use `list()` to collect different categories of vectors. For example, if we want to create two categories, positive and negative, to categorize the text, we can write it as `dictionary(list(positive = ..., negative = ...))`. Inside each category, we use quotation marks (`""`)to specify multiple words under one category, for example: `dictionary(list(positive = c("happy", "smile"), negative = c("unhappy")))`. An asterisk (`*`) can be used to match all variations of a root word. For example, happ* can include happiness and happy.

Task: 
(1) Create a dictionary with two categories, school and art. The words that belong to school include school, child, student, and campus. The words that belong to art include art, museum, and perform.

``` {r include = TRUE}


```

## Step 4: Applying the dictionary to our tokenized data
token_lookup() is the most flexible dictionary look up function in quanteda. Simply out, it is used to match tokens to a dictionary, check whether certain token appears in a dictionary. We can write it as `token_lookup(token object, dictionary = dictionary object)`.

Task: 
(1) Apply the dictionary you created to a tokenized object
``` {r include = TRUE}


```


## Applying Dictionaries & Document-Feature Matrices with dfm()
- A Document-Feature matrix (DFM) provides frequencies of features (our dictionary keyword category groups) for each document (snippet) in our data.
- We can use DFMs to plot and visualize our data and help us analyze sentiments or the distribution of topics captured in a set of text-based data.

Task:
(1) Nest the tokens_lookup() object into the dfm() command and turn your results into a data.frame.

``` {r include = TRUE}


```


