---
title: "JOUR 8500 CARET Demo"
author: "Eunsun & Namuun"
date: "`r Sys.Date()`"
output: html_document
---
## About caret

caret stands for Classification And Regression Training. It is an R package that streamlines the process of building machine learning models.

The main advantage of caret is that it provides a consistent interface for fitting many different models. Instead of learning separate syntax for each algorithm (e.g., random forest, k-nearest neighbors, SVM), we can use the same train() function and simply change the method argument.

This makes it easy to:

- Fit multiple models
- Compare performance
- Perform cross-validation
- Tune hyperparameters
- Evaluate results in a standardized way

In our case, we use caret to fit a random forest model to predict whether there is higher sales based on ad expenditure.

To learn more about caret, please visit https://topepo.github.io/caret/index.html

```{r echo=TRUE, message=FALSE, warning=FALSE, results='hide'}
# prepare packages
if (!require("caret")) install.packages("caret")
if (!require("ranger")) install.packages("ranger")
if (!require("tidyverse")) install.packages("tidyverse")
if (!require("e1071")) install.packages("e1071")

# Load packages
library(caret)
library(ranger)
library(tidyverse)
library(e1071)

# Load dataset
ad_data <- read.csv("https://raw.githubusercontent.com/selva86/datasets/master/Advertising.csv")

# remove the index column
ad_data <- ad_data[, -1]

# check dataset if index column is removed
head(ad_data)

# add a logical variable for "high-sales" (sales > median)
ad_data <- ad_data %>%
  mutate(high_sales = sales > median(sales)) %>%
  # remove the original "sales" variable
  select(-sales)

table(ad_data$high_sales)

# split into training and testing
set.seed(123)
train_index <- sample(1:nrow(ad_data), 0.9 * nrow(ad_data)) 
ad_train <- ad_data[train_index, ]
ad_test  <- ad_data[-train_index, ]

# remove the original dataset
rm(ad_data)

# view the first 6 rows of the training data
head(ad_train)
```
It looks like we have 180 ads:

```{r echo=TRUE}
dim(ad_train)
```

Time to fit a random forest model using caret. Anytime we want to fit a model using train() we tell it which model to fit by providing a formula as the first argument.

as.factor(high_sales) ~ . means that we want to model high_sales (whether an advertising expenditure generated high sales or not) as a function of all of the other variables in the dataset (TV, radio, and newspaper spending).

Then we need to provide a method. We specify "ranger" to implement a random forest model.

```{r echo=TRUE}
# fit a random forest model (using ranger)
rf_fit <- train(as.factor(high_sales) ~ ., 
                data = ad_train, 
                method = "ranger"
)
```
By default, the train function without any arguments re-runs the model over 25 bootstrap samples and across 3 options of the tuning parameter (the tuning parameter for ranger is mtry; the number of randomly selected predictors at each cut in the tree).

```{r echo=TRUE}
rf_fit
```
To test the data on an independent test set is equally as simple using the inbuilt predict function.

```{r echo=TRUE}
# predict the outcome on the test set
ad_rf_pred <- predict(rf_fit, ad_test)

# compare predicted outcome and true outcome
confusionMatrix(ad_rf_pred, as.factor(ad_test$high_sales))
```
The random forest model achieved 95% accuracy on the test set, substantially outperforming chance (50%) and showing strong agreement beyond chance (Kappa = 0.90). However, because the test sample is small (n = 20), these results should be interpreted with caution.

## Cross-Validation with trainControl()

So far, we evaluated our model using one train/test split. However, results can vary depending on how the data is split. A more stable way to evaluate model performance is cross-validation.

In k-fold cross-validation, the training data is split into k parts (folds). The model is trained on k−1 folds and validated on the remaining fold. This process repeats k times, and the results are averaged.

# Exercise: Question 1-3
In this exercise, we will apply k-fold cross-validation using `method = "cv"`.
If you want to split the training data into K folds and perform validation, use the following code:

fit_control <- trainControl(method = "cv",
                            number = K)

Using this setup, answer Questions 1–3.
The remaining steps follow the same procedure as previously introduced.
# Question 1
```{r echo=TRUE}
# specify 10-fold cross-validation
fit_control <- trainControl(method = "cv",
                            number = 10)
```
# Question 2
Then, ensure reproducibility by setting the seed as 825 (You can use any numbers for seed)
```{r echo=TRUE}
set.seed(825)
```
# Question 3
Finally, train a Random Forest classification model using the `ranger` method with 10-fold cross-validation on the training data and display the results.
```{r echo=TRUE}
rf_cv_fit <- train(as.factor(high_sales) ~ ., 
                   data = ad_train, 
                   method = "ranger",
                   trControl = fit_control)

rf_cv_fit
```

## Other Classification Methods

One advantage of caret is that we can easily try different classification algorithms by simply changing the method argument in train().

The formula and data stay exactly the same — only the method changes.

```{r echo=TRUE}
set.seed(123)

# Logistic Regression
fit_glm <- train(as.factor(high_sales) ~ ., 
                 data = ad_train, 
                 method = "glm",
                 trControl = fit_control)

# K-Nearest Neighbors
fit_knn <- train(as.factor(high_sales) ~ ., 
                 data = ad_train, 
                 method = "knn",
                 trControl = fit_control)

fit_glm
fit_knn
```

## Resampling options

Many machine learning models have tuning parameters that affect performance. To choose good parameter values, we use resampling methods such as cross-validation. In caret, the trainControl() function specifies how resampling is performed and is passed into train().

```{r}
# specify 10-fold cross-validation
fit_control <- trainControl(method = "cv",
                            number = 10)
```

```{r echo=TRUE}
# run a random forest model
set.seed(825)

rf_fit <- train(as.factor(high_sales) ~ ., 
                data = ad_train, 
                method = "ranger",
                trControl = fit_control)
rf_fit
```

## Model parameter tuning options

Now instead of letting caret automatically choose tuning parameters, we manually define a tuning grid.

```{r echo=TRUE}
# define a grid of parameter options to try
rf_grid <- expand.grid(
  mtry = c(1, 2, 3),                  # cannot exceed number of predictors
  splitrule = c("gini", "extratrees"),
  min.node.size = c(1, 3, 5)
)

rf_grid
```

```{r echo=TRUE}
rf_fit <- train(as.factor(high_sales) ~ .,
                data = ad_train,
                method = "ranger",
                trControl = fit_control,
                tuneGrid = rf_grid)
rf_fit
```

